|

### 2025-01-30 doc/paper.qmd
prep

7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure the inclusion of trading days around earnings announcements.

>>>>

7. To account for non-trading days in Datastream, I extend the event window from (-1, +1) to (-3, +3) to ensure higher inclusion of trading days around earnings announcements.
